Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-03-18 Writing/CEA_3rd_round/replies_rev.rmd
Edits by TM on many fronts.

<span style="color:blue">  
Please see Figure E.1 in Appendix E that shows the convergence of CNN for a single simulation round. We cannot show this kind of figure for all the simulation rounds. But, any interested readers can replicate our work as the codes will be accessible publicly.
</span>

@@

We actually realized the results presented in Figure 6 is completely invalid. As you pointed out the problem with the relationship presented in the figure is basically comparing apples and oranges. The biggest problem of the relationship we identified is that the maximum profit of the field is very different across simulations (the field in some simulations are simply more profitable than the fields in other simulations). So, basically, the observed variation in achieved profits by estimated site-specific EONR is dominated simply by how profitable fields are on average. For this reason, we eliminated the figure and also dropped our claim that yield prediction and EONR prediction are uncorrelated. Thank you so much for spotting this embarrassing mistake from our side.

However, please note that our claim that better yield prediction does "not necessarily" lead to higher profit remains intact. This is evident in Table 1 and the analysis behind this table is valid. This happens because you can predict yield well for a "wrong" reason, attributing parts of variations in yield to something other than its true driver.

approximating yield response function , predicting yield levels at the observed points

Estimating the structure well leads to a better prediction of yield, however better prediction of yield does not necessarily mean a better prediction of the structure of the yield response function (yield response curve) because you can predict yield levels at the observed rate for wrong reasons.

@@

<span style="color:blue">  
Please see page xx, line xx for a new list of studies that attempt to estimate EONR. Please note that this study has no interest in studies that just predict yield without trying to show how they can use it for EONR estimation. Prediction of yield is almost always not the goal of farmers. We are listing studies that predict yields (or estimate yield response function to be more precise) and then predict EOIR based on them. Also, there is no study that test the performance of EONR using real data. This is because that is fundamentally impossible as we mentioned above. There are studies that predict field-level (not site-specific within a field) EONR for individual fields one by one using a traditional regression approach, then model EONR using ML methods to see how close their estimated field-level EONRs from the trained ML methods are to the EONR "estimated" for individual fields (Shun cite a paper that does this). But, please note that the field-level EONRs they compare against are "estimated." Why did they "estimate" EONR for each field? That is because they do not (and will never) know the true EONR for each field. Moreover, the objective of such studies are fundamentally different from ours. Our focus is on site-specific EONR within a field, theirs' are on field-specific EONR. We consider those studies not very relevant. Including those studies will simply bloat the introduction. 
</span>

@@

>>>>

<span style="color:blue">  
Please see Figure E.1 in Appendix E that shows the convergence of CNN for a single simulation round. We cannot show this kind of figure for all the simulation rounds. But, any interested readers can replicate our work as the codes will be accessible publicly. Please also see the figure below. CNN severely underestimates the impact of N and estimated yield response to N is almost flat, but not exactly flat.
</span>

@@

We actually realized the results presented in Figure 6 (in the previous round) is completely invalid. As you pointed out the problem with the relationship presented in the figure is basically comparing apples and oranges: comparing across simulation rounds. Figure 8 plots RMSE of yield and EONR predictions by model and simulation round for several simulation rounds. Figure 6 in the previous round was basically mixing RMSE from all the simulation rounds and finding R^2 of the two relationshiop. That is why R^2 was extremely low. Therefore, we decided to remove the figure entirely. Also, we do not claim that yield and EONR predictions are not correlated at all as we realized that it is a false claim. Thank you so much for saving us from claiming the false statement.

However, please note that our claim that better yield prediction does "not necessarily" lead to higher profit remains intact. According to your suggestions, we provide much more in-depth discussions about why that is the case under section 4.2. As you suggested, models that can recover the "structure" of the yield response function will perform well in predicting EONR. However, you can predict yield leves at the observed rates (rates that are actually applied in the experiment) without recovering the structure of the yield response function well. The training process of prediction-oriented ML methods may twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits its primary obejective of predicting yield levels well at the "observed" nitrogen rate for each site well. Please see our more detailed discussions on this matter in section 4.2.

We understand your suggestion of running simulations under different magnitude of erorr comes from your doubt about why yield and EONR prediction is not correlated. But, ee conducted simulations with different degrees of error anyway. **The results are shown in Appendix**.

@@

<span style="color:blue">  
Please see page xx, line xx for a new list of studies that attempt to estimate EONR. Please note that this study has no interest in studies that just predict yield without trying to show how they can use it for EONR estimation. Prediction of yield is almost always not the goal of farmers. We are listing studies that predict yields (or estimate yield response function to be more precise) and then predict EOIR based on them. Also, there is no study that tests the performance of EONR using real data. This is because that is fundamentally impossible as we mentioned above. There are studies that predict field-level (not site-specific within a field) EONR for individual fields one by one using a traditional regression approach, then model EONR using ML methods to see how close their estimated field-level EONRs from the trained ML methods are to the EONR "estimated" for individual fields (Shun cite a paper that does this). But, please note that the field-level EONRs they compare against are "estimated." Why did they "estimate" EONR for each field? That is because they do not (and will never) know the true EONR for each field. Moreover, the objective of such studies are fundamentally different from ours. Our focus is on site-specific EONR within a field, theirs' are on field-specific EONR. We consider those studies not very relevant. Including those studies will simply bloat the introduction. 
</span>

@@

<span style="color:blue">  
We already discuss our results to the state of the art of the literature. The state of the art is sadly trying to predict yield as well as possible. We show that such practice can be misleading when your goal is to actually help farmers with making nitrogen application decisions (predicting EONR well). There is nothing wrong with our approach in yield prediction as evident in Figure 12. We are using ML methods that have been used in the literature of OFE for site-specific input management. Those studies were published very recently. We added our description about how the size of epsilon affects our results briefly at line xx, page yy. But, it is imporatnt to realize that all the models uses the same data. That is the models are competing against each other on the even ground. Changing the size of error has little effect on the comparative advantage of CF over other models much.

### 2022-03-18 Writing/appendix.rmd
Edits by TM on many fronts.

## Appendix E: CNN performance per training epoch
The below figure shows training and validation loss measured by mean square error (MSE) over the number of epochs in a single simulation round under aabbyytt scenario.

@@

## Appendix F: MB-yield response curves
The below figure shows some examples of site-specific Mitscherlich-Baule yield function to illustrate how yield responds to N.

```{r vis-MB-curve, fig.cap = "Figure F.1: Examples of Mitscherlich-Baule yield response curve"}
vis_MB_curve
```

## Appendix G: The difference between predicting yields and predicting change in yields

```{r, vis-MB-BRF-y, fig.cap = "Figure G.1: Predicted (scenario: aby)"}
vis_MB_BRF_y
```

>>>>

## Appendix E: CNN performance per training epoch
The figure below shows training and validation loss measured by mean square error (MSE) over the number of epochs in a single simulation round under aabbyytt scenario for CNN as an illustration. For readers interested in knowing how CNN is trained for all the simulation rounds, please see the python program available at a Mendeley dataset [@Kakimoto2022codes] or a Github repository at https://github.com/Shunkei3/VRA_with_CF.git.)

@@

### 2022-03-18 Writing/manuscript_cea.rmd
Edits by TM on many fronts.

The first term on the right-hand side of Eq. \@ref(eq:eqn3) is the deterministic yield component. The variable $N$ represents the nitrogen fertilizer application rate (kg/ha) which the trial designs varied by plot. Also in Eq. \@ref(eq:eqn3), $\alpha$, $\beta$, and $ymax$ are spatially varying parameters that govern how yield level is determined in conjunction with the applied N rate. They reflect local cell-level production conditions, such as soil characteristics and topography. For example, $\alpha$, which represents what the yield would be when no nitrogen is applied in conjunction with $ymax$, may reflect soil organic matter and residual nitrogen from previous year's production. $ymax$, which determines the maximum yield attainable, may include other micro nutrients like phosphorus and soil depth. $\beta$ can be interpreted as reflecting how efficiently the crop uses N to create grain mass, and might depend on soil properties that affect the availability of applied N fertilizer to the crop, say due to N immobilization, leaching, denitrification, and volatilization [@johnson2005nitrogen; @alva2006nitrogen]. The error term of the yield $\varepsilon$ represents the composite of all the unobserved factors that affect crop yield beyond $\alpha$, $\beta$, $ymax$ and $N$. Each cell $(i,j)$'s "true" optimal N application rate, denoted $N^{opt}_{i,j}$, was calculated by solving a profit maximization problem by cell assuming that the prices of corn and N fertilizer were $\$0.138/kg$ and $\$1.323/kg$, respectively. These prices are used consistently for our simulations. See Appendix C.1 for further details on how the paremeters were generated and sample maps of the parameters and true economically optimal N rates.

@@

CNN leaves room for researchers to determine its architecture. We used a slightly modified version of one of the multi-stream CNN architectures proposed by @barbosa2020modeling, called "Late Fusion." Briefly stated, explanatory variables except N rate (e.g. $\alpha_{i,j}$, $\beta_{i,j}$, etc.) entered the model as a set of $6 \times 6$ element rasters.The input size of the N rate is treated as $1 \times 1$ because it is spatially homogeneous within each subplot. First, each input was connected to an independent convolutional layer with eight $3 \times 3$ filters each with stride one, followed by a $2 \times 2$ max-pooling layer with stride two. Then, a fully-connected rectified linear unit (ReLU) layer with sixteen neurons was added after each max-pooling layer, followed by a single ReLU neuron. Finally, multiple neurons were concatenated and fed to the fully-connected ReLU layer with sixteen neurons, followed by an output with a linear activation function. @barbosa2020modeling demonstrated that among several CNN architectures, this architecture modeled crop yield response to N rate management best. CNN was implemented in Python v3.7.6 using Pytorch v1.7.0 [@paszke2017automatic]. The Adam optimizer [@kingma2014adam] was used with a learning rate of $0.001 \%$ (default value). To avoid over-fitting, early stopping was used to monitor validation loss with a ten epochs of patience.

@@

Table \@ref(tab:table-y) shows the mean RMSE of yield prediction over the one thousand simulations. Since CF-base does not predict yield, the table only reports the results from RF, BRF and CNN. Compared to the result of EONR estimation, RF performed as well as BRF in the simple modeling scenarios of "aby" and "abytt." This fact along with the poor performance of RF in predicting EONR presented in \@ref(tab:table-optN) show that strong predictive power of yield levels does not imply accurate prediction of EONR. Further, RF shows vulnerability to the inclusion of many correlated variables, as is displayed for EONR prediction as well. While CNN performed worse than RF and BRF in "aby" and "abytt," it performed better than RF in more complicated modeling scenarios, showing robustness, at least in yield prediction, to inclusion of many correlated variables. Of course, while on average in the "aabbyy" and "aabbyytt" scenarios CNN predicted yields better than RF did, CNN's EONR predictions were worse than RF's, which further backs our claim that a good yield prediction capability does not imply good EONR prediction capability.

@@

Table \@ref(tab:xxx) illustrates the distinction between yield prediction and yield response function prediction.

In essence, good performance in predicinting yield "levels" at the observed points does not mean good performanc ein predicting yield response function, which is about finding out what "would" happen to yield if rates other than the one actually applied were applied. This happens because you can predict yield leves for wrong reasons by giving wrong amount of credit to wrong drivers (variables) of yield levels. This is because prediction-oriented ML methods focus on predicting yield levels well at the "observed" points, but not the points that were not seen. This is by construction because they are trained to minimize the error in yield "level" prediction at the "observed" points. In contrast, CF focuses to recover the yield response functions well (or alternatively the causal impact of N on yield at different discrete rates of N). Our results how that this distinction between prediction-oriented ML methods and CF can result in economically meanigful difference, where CF outperforms.

All previous research has followed a two-step procedure to estimate site-specific EONRs. The first step was to select the model that predicts yield most accurately, and the following step used the selected model to predict EONR. Table \@ref(tab:count-table) shows that following this process led to the choice of the best (as measured by profit) EONR prediction model in fewer than $30\%$ of the "aby" and "abytt" simulation rounds, $40\%$ of the "aabbyy" simulation rounds, and $50\%$ of the "aabbyytt" simulation rounds. For example, the table shows that, in the "aby" scenario, RF attained the lowest RMSE for yield prediction in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` of 1000 iterations, and attained the lowest $\hat{\pi}_{def}$ in `r summary_res_CNN_RF_BRF[Model=="aby", count_RF]` of those `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` iterations. That is, in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]-summary_res_CNN_RF_BRF[Model=="aby", count_RF]` out of `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` rounds, the RF model performed the best at yield prediction among RF, BRF, and CNN, but did not provide EONR estimates that led to the highest profit. Similarly, in no case did the CNN method provide both the best yield prediction and the best EONR estimation simultaneously. In the rounds in which BRF predicted yield best, the two-step process worked well. For example, Table \@ref(tab:count-table) shows that BRF predicted EONR best in `r summary_res_CNN_RF_BRF[Model=="aby", count_BRF]` of the `r summary_res_CNN_RF_BRF[Model=="aby", count_y_BRF]` "aby" simulation rounds in which it predicted yields best. But BRF predicted yields best in fewer than $30\%$ of the rounds, implying that the two-step procedure failed more than $70\%$ of the time.

@@

We examined the use of CF in the generation of site-specific input management recommendations. Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONRs to those of the prediction-oriented ML methods RF, BRF, and CNN. CF consistently outperformed the other methods across all the modeling scenarios in terms of EONR prediction and profit generation. Also, it is notable that RF's performance in EONR prediction was considerably worse than BRF.  Examining the relative performance of CF to the other ML methods in different contexts will be an interesting and fruitful future research.

@@

This research was supported by a USDA-NIFA-AFRI Food Security Program Coordinated Agricultural Project, titled "Using Precision Technology in On-farm Field Trials to Enable Data-Intensive Fertilizer Management," (Accession Number 2016-68004-24769), and also by the a USDA-NRCS Conservation Innovation Grant from the On-farm Trials Program, titled "Improving the Economic and Ecological Sustainability of US Crop Production through On-Farm Precision Experimentation" (Award Number NR213A7500013G021).

>>>>

The first term on the right-hand side of Eq. \@ref(eq:eqn3) is the deterministic yield component. The variable $N$ represents the nitrogen fertilizer application rate (kg/ha) which the trial designs varied by plot. Also in Eq. \@ref(eq:eqn3), $\alpha$, $\beta$, and $ymax$ are spatially varying parameters that govern how yield level is determined in conjunction with the applied N rate. They reflect local cell-level production conditions, such as soil characteristics and topography. For example, $\alpha$, which represents what the yield would be when no nitrogen is applied in conjunction with $ymax$, may reflect soil organic matter and residual nitrogen from previous year's production. $ymax$, which determines the maximum yield attainable, may include other micro nutrients like phosphorus and soil depth. $\beta$ can be interpreted as reflecting how efficiently the crop uses N to create grain mass, and might depend on soil properties that affect the availability of applied N fertilizer to the crop, say due to N immobilization, leaching, denitrification, and volatilization [@johnson2005nitrogen; @alva2006nitrogen]. Figure \@ref(fig:vis-MB-curve) presents example visualization of site-specific yield response fuctions for some sites.

```{r vis-MB-curve, fig.cap = "Figure F.1: Examples of Mitscherlich-Baule yield response curve"}
vis_MB_curve
```

The error term of the yield $\varepsilon$ represents the composite of all the unobserved factors that affect crop yield beyond $\alpha$, $\beta$, $ymax$ and $N$. Each cell $(i,j)$'s "true" optimal N application rate, denoted $N^{opt}_{i,j}$, was calculated by solving a profit maximization problem by cell assuming that the prices of corn and N fertilizer were $\$0.138/kg$ and $\$1.323/kg$, respectively. These prices are used consistently for our simulations. See Appendix C.1 for further details on how the paremeters were generated and sample maps of the parameters and true economically optimal N rates.

@@

CNN leaves room for researchers to determine its architecture. We used a slightly modified version of one of the multi-stream CNN architectures proposed by @barbosa2020modeling, called "Late Fusion." Briefly stated, explanatory variables except N rate (e.g. $\alpha_{i,j}$, $\beta_{i,j}$, etc.) entered the model as a set of $6 \times 6$ element rasters.The input size of the N rate is treated as $1 \times 1$ because it is spatially homogeneous within each subplot. First, each input was connected to an independent convolutional layer with eight $3 \times 3$ filters each with stride one, followed by a $2 \times 2$ max-pooling layer with stride two. Then, a fully-connected rectified linear unit (ReLU) layer with sixteen neurons was added after each max-pooling layer, followed by a single ReLU neuron. Finally, multiple neurons were concatenated and fed to the fully-connected ReLU layer with sixteen neurons, followed by an output with a linear activation function. @barbosa2020modeling demonstrated that among several CNN architectures, this architecture modeled crop yield response to N rate management best. CNN was implemented in Python v3.7.6 using Pytorch v1.7.0 [@paszke2017automatic]. The Adam optimizer [@kingma2014adam] was used with a learning rate of $0.001 \%$ (default value). To avoid over-fitting, early stopping was used to monitor validation loss with a ten epochs of patience (see Figure \@ref(cnn-epoch) for an illustration of the convergens of training with respect to the number of epochs).

@@

Table \@ref(tab:table-y) shows the mean RMSE of yield prediction over the one thousand simulations (see Figure \@ref(fig:vis-y-pred) in Appendix xx for example visualizations of predicted and true yields along with RMSE values by model). Since CF-base does not predict yield, the table only reports the results from RF, BRF and CNN. Compared to the result of EONR estimation, RF performed as well as BRF in the simple modeling scenarios of "aby" and "abytt." This fact along with the poor performance of RF in predicting EONR presented in \@ref(tab:table-optN) show that strong predictive power of yield levels does not imply accurate prediction of EONR. Further, RF shows vulnerability to the inclusion of many correlated variables, as is displayed for EONR prediction as well. While CNN performed worse than RF and BRF in "aby" and "abytt," it performed better than RF in more complicated modeling scenarios, showing robustness, at least in yield prediction, to inclusion of many correlated variables. Of course, while on average in the "aabbyy" and "aabbyytt" scenarios CNN predicted yields better than RF did, CNN's EONR predictions were worse than RF's, which further backs our claim that a good yield prediction capability does not imply good EONR prediction capability.

@@

Figure \@ref(fig:vis-MB-BRF-y) illustrates the distinction between yield prediction at observed points and yield response function prediction, giving insights into why good yield prediction does not necessarily lead to good EONR prediction in general. The black curves are the true yield response functions for two sites in a single simulation round. Red symbols represent true (circle) or predicted (triangle) yields at the rate observed in the data: the rate that was actually applied in the experiment. That is, 150 kg/ha was applied to the two sites in the experiment. Blue symbols represent true (circle) or predicted (triangle) yield at some rates that were not observed (or applied) for the two sites in the experiment. Prediciton-oriented ML methods train models to minimize errors in yield level prediction at the "observed" rates (red points). Both RF- and BRF-trained models predict yield level at the observed rate well for the two sites (the vertical distance between the red circle and triangle). However, as you move away from the observed N rate, yield prediction errors tend to become larger (of course smaller yield prediction erros can be observed at unobserved rates some times). More important, connecting the predicted yield points does not trace the true yield response curves well for both RF and BRF. Specifically, in this example, the predicted impact of N on yield from RF and BRF are both smaller than the true impact of N.

```{r, vis-MB-BRF-y, fig.width=7, fig.height=5, fig.cap = "The difference between yield level prediction and yield response prediction (scenario: aabbyytt)"}
vis_MB_BRF_y
```

In essence, Figure \@ref(fig:vis-MB-BRF-y) illustrats that good performance in predicinting yield "levels" at the "observed" points does not mean good performanc in predicting yield "response" function, which is about finding out what "would" happen to yield if rates other than the one actually applied were applied. This happens because you can predict yield "levels" for wrong reasons by giving wrong amount of credit to wrong drivers (variables) of yield levels. The training process of prediction-oriented ML methods may twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits its primary obejective of predicting yield levels well at the "observed" nitrogen rate for each site well. This problem is also observable at Figure \@ref(fig:plot-tre), which shows both RF and BRF understimates the impact of N on yield: or in other words, their predicted site-speific yield response functions tend to be flatter than they truelly are. Of course, the CNN approach in our study is an extreme case where it completley fails to recognize the contribution of N on yield. But, remember that CNN does performs almost as good as RF and BRF in yield prediction as shown in Table \@ref(tab:table-y).

Since you need to be able to estimate yield curves (yield response function) well at the site level to predict site-specific EONR (not yield level) well, models' ability to predict yield levels well at the observed rates does not guarantee their ability to predict site-specific EONR well. In contrast to RF, BRF, and CNN, CF focuses to recover the yield response functions well (or alternatively the causal impact of N on yield at different discrete rates of N). We showed that CF can predict the impact of N on yield when N is chaned from an unobserved rate to another unobserved rats as shown in Figure \@ref(fig:plot-tre), which then translated to better performance in predicting EONR and profit.

All previous research has followed a two-step procedure to estimate site-specific EONRs. The first step was to select the model that predicts yield leves most accurately at the observed points, and the following step used the selected model to predict EONR. As discussed ealier, this practice can be economically harmful. Figure \@ref(fig:vis-RMSE-y-eonr) further illustrates the underlying problem. It plots RMSE of yield (x-axis) and EONR (y-axis) predictions by model and simulation round for several simulation rounds. As you can see clearly, the model with the lowest yield RMSE is not necessarily the model with the lower EONR RMSE for a given simulation round (simulation round xx and yy).

```{r, vis-RMSE-y-eonr, fig.width=5, fig.height=5, fig.cap = "Figure I.1: The Relationship between Yield and EONR Prediction Performances ((scenario: aabbyytt)"}
vis_RMSE_y_eonr
```

Table \@ref(tab:count-table) summarizes the relationship between yield and EONR prediction RMSE for all the simulation rounds. It shows clearly that following the process would lead to the choice of the best (as measured by profit) EONR prediction model in fewer than $30\%$ of the "aby" and "abytt" simulation rounds, $40\%$ of the "aabbyy" simulation rounds, and $50\%$ of the "aabbyytt" simulation rounds. For example, the table shows that, in the "aby" scenario, RF attained the lowest RMSE for yield prediction in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` of 1000 iterations, and attained the lowest $\hat{\pi}_{def}$ in `r summary_res_CNN_RF_BRF[Model=="aby", count_RF]` of those `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` iterations. That is, in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]-summary_res_CNN_RF_BRF[Model=="aby", count_RF]` out of `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` rounds, the RF model performed the best at yield prediction among RF, BRF, and CNN, but did not provide EONR estimates that led to the highest profit. Similarly, in no case did the CNN method provide both the best yield prediction and the best EONR estimation simultaneously. In the rounds in which BRF predicted yield best, the two-step process worked well. For example, Table \@ref(tab:count-table) shows that BRF predicted EONR best in `r summary_res_CNN_RF_BRF[Model=="aby", count_BRF]` of the `r summary_res_CNN_RF_BRF[Model=="aby", count_y_BRF]` "aby" simulation rounds in which it predicted yields best. But BRF predicted yields best in fewer than $30\%$ of the rounds, implying that the two-step procedure failed more than $70\%$ of the time.

@@

We examined the use of CF in the generation of site-specific input management recommendations. Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONRs to those of the prediction-oriented ML methods RF, BRF, and CNN. CF consistently outperformed the other methods across all the modeling scenarios in terms of EONR prediction and profit generation. Also, it is notable that RF's performance in EONR prediction was considerably worse than BRF. It is importnat to keep in mind that we are not claiming that CF always performs better economically than RF, BRF, and CNN. Examining the relative performance of CF to the other ML methods in different contexts will be an interesting and fruitful future research.

@@

We thank Scott Swinton at Michigan State University for providing helpful comments on this publication. This research was supported by a USDA-NIFA-AFRI Food Security Program Coordinated Agricultural Project, titled "Using Precision Technology in On-farm Field Trials to Enable Data-Intensive Fertilizer Management," (Accession Number 2016-68004-24769), and also by the a USDA-NRCS Conservation Innovation Grant from the On-farm Trials Program, titled "Improving the Economic and Ecological Sustainability of US Crop Production through On-Farm Precision Experimentation" (Award Number NR213A7500013G021).
